---
title: "Bootstrap Confidence Intervals"
author: ""
date: ""
output: 
  html_document
---

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE,
                      comment = "#>", highlight = TRUE,
                      fig.align = "center")
```


# Packages and Data

```{r packages}
library(tidyverse)
library(infer)
```

Consider 20 1 bedroom apartments that were randomly selected on 
Craigslist Manhattan from apartments listed as "by owner."

```{r read_data}
manhattan <- read_csv("data/manhattan.csv")
```

# Exercises

## Exercise 1

Create a 90% bootstrap confidence interval for the population median price of
1 bedroom apartments in Manhattan.

## Exercise 2

Create a 98% bootstrap confidence interval for the population mean price of
1 bedroom apartments in Manhattan. Write out an appropriate interpretation of
this interval.

## Exercise 3

Compare the two confidence intervals. Which interval is wider?

## Exercise 4

Can we use these intervals to make an accurate statement about the mean/median 
price of 1 bedroom apartments in the *Bronx*?

## Stage, commit and push

1. Stage your modified files.
2. Commit your changes with an informative message.
3. Push your changes to your GitHub repo.
4. Verify your files were updated on GitHub.
